Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating

### 2017-09-29 SubGenome Analysis.Rmd
Isoform dominance plot

# source("~/git/SubGenomes/R/parseSubgenomes.R")
# source("~/git/SubGenomes/R/addGOTerms.R")
# source("~/git/SubGenomes/R/parseGOSlim.R")
# source("~/git/SubGenomes/R/createTopGO.R")
# source("~/git/SubGenomes/R/parseExpressionData.R")

# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\loadData.R")
# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\cleanData.R")
# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\parseSubgenomes.R")
# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\addGOTerms.R")
# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\parseGOSlim.R")
# # source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\createTopGO.R")
# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\parseExpressionData.R")

library(topGO)
library(readr)
library(readxl)
library(ggplot2)
library(tidyr)
library(dplyr)
library(VennDiagram)
library(gridExtra)

# topGO::groupGOTerms()
# MFterms <- ls(GOMFTerm)
# BPterms <- ls(GOBPTerm)
# CCterms <- ls(GOCCTerm)
```

@@

```{r subgenome_protein_dominance, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=10, fig.height=6, fig.align='center'}
plot <- graphGenePairDominanceByExperiment(maize.protein.abundance.sample.avg, homeologs.pairs, 4, FALSE)
plot + labs(title = paste0("Which homeolog dominates protein abundance? (factor=",4,")"))
plot(plot)
```

@@

The results of this report are available at **`r params$outputFile`**.

```{r writeSubgenomesToFile, echo=FALSE}
## Now recover which genes are in these sets
#write.table(subgenome, params$outputFile, sep="\t")
```

>>>>

library(topGO)
library(readr)
library(readxl)
library(ggplot2)
library(tidyr)
library(dplyr)
library(VennDiagram)
library(gridExtra)
```

@@

```{r subgenome_protein_dominance, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=10, fig.height=6, fig.align='center'}
factor <- 4
plot <- graphGenePairDominanceByExperiment(maize.protein.abundance.sample.avg, homeologs.pairs, factor, FALSE) + 
  labs(title = paste0("Which homeolog dominates protein abundance? (factor=",factor,")"))
plot(plot)
```

Isoforms also follows this dominance patter.

```{r subgenome_isoform_dominance, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=6, fig.height=4, fig.align='center'}
## Plot frequency of isoform counts for each gene
plot <- graphGenePairDominanceByIsoForms(geneTranscript.counts, homeologs.pairs, 4)
plot(plot)
```

@@
